HUME: Human UCCA-Based Evaluation of Machine Translation

### 2016-06-03 paper/main.tex
shorten a bit

To assess HUME reliability for long sentences,
we binned the sentences according to length and measured Kappa on each of the
bins (\figref{fig:iaalength}).
%The Kappas for each bin is presented in 
%\figref{fig:iaalength}.
%Results show that there is
We see
no discernable reduction of IAA with sentence
length. Also, from \tabref{tab:iaa} the overall IAA
is quite similar for all languages, showing good agreement (0.6--0.7).
However, there are differences observed when we break down by node type.
In particular, we see a contrast  between
Czech and Polish, where the IAA is higher for atomic than for structural units, and German and Romanian,
where the reverse is true. We also observe low IAA (around 0.3) in the cases of
German atomic units, and Polish and Czech structural units.

@@

Figure~\ref{fig:dacorrelationtypes} presents an analysis of HUME's correlations with DA by HUME unit type,
an analysis enabled by HUME's semantic decomposition. 
Each bar represents a correlation between HUME and an aggregate HUME score
based on a sub-set of the units (\#nodes for the en-de/en-ro setting in brackets):
all units ('all', 8624/10885), atomic ('atomic', 5417/6888) and structural units ('struct', 3207/3997),
and units by UCCA categories: Scene main relations (i.e, Process and State units; 'P and S', 954/1178), Parallel Scenes ('H', 656/784),
Participants ('A', 1348/1746),
Centres ('C', 1904/2474), elaborators ('E', 1608/2031) and linkers ('L', 261/315).
In both settings correlation is highest in the 'all' case, supporting our claim for the value of aggregating over a wide range of semantic phenomena. Some types of nodes predict the DA scores better than others. HUME scores on As correlate more strongly with DA than scores on Scene Main Relations (P+S). Center nodes (C) are also more correlated than elaborator nodes (E), which is expected given that Centers are defined to be more semantically dominant. Future work will construct an aggregate HUME score which weights the different node types according to their semantic relevance.

>>>>

To assess HUME reliability for long sentences,
we binned the sentences according to length and measured Kappa on each bin
(\figref{fig:iaalength}).
%The Kappas for each bin is presented in 
%\figref{fig:iaalength}.
%Results show that there is
We see
no discernible reduction of IAA with sentence
length. Also, from \tabref{tab:iaa} the overall IAA
is similar for all languages, showing good agreement (0.6--0.7).
However, there are differences observed when we break down by node type.
Specifically, we see a contrast  between
Czech and Polish, where the IAA is higher for atomic than for structural units, and German and Romanian,
where the reverse is true. We also observe low IAA (around 0.3) in the cases of
German atomic units, and Polish and Czech structural units.

@@

Figure~\ref{fig:dacorrelationtypes} presents an analysis of HUME's correlations with DA by HUME unit type,
an analysis enabled by HUME's semantic decomposition. 
Each bar represents a correlation between HUME and an aggregate HUME score
based on a sub-set of the units (\#nodes for the en-de/en-ro setting in brackets):
all units ('all', 8624/10885), atomic ('atomic', 5417/6888) and structural units ('struct', 3207/3997),
and units by UCCA categories: Scene main relations (i.e, Process and State units; 'P and S', 954/1178), Parallel Scenes ('H', 656/784),
Participants ('A', 1348/1746),
Centres ('C', 1904/2474), elaborators ('E', 1608/2031) and linkers ('L', 261/315).
In both settings correlation is highest in the 'all' case, supporting our claim for the value of aggregating over a wide range of semantic phenomena. Some types of nodes predict the DA scores better than others. HUME scores on As correlate more strongly with DA than scores on Scene Main Relations (P+S). Center nodes (C) are also correlate more than than elaborators (E), which is expected given that Centers are defined to be more semantically dominant. Future work will construct an aggregate HUME score which weights the different node types according to their semantic relevance.
